### 2024-05-18 fantasy-football.qmd
20240518 - video intro to fantasy football
20240518 - updates

@@

- receptions (called "points per reception" [PPR] leagues)
- return yards
- passing attempts
- rushing attempts

>>>>

::: {.content-visible when-format="html"}

![Video that provides introduction to fantasy football](images/fantasyFootball.mp4){width=100%}

:::

@@

- receptions (called "point per reception" [PPR] leagues)
- return yards
- passing attempts
- rushing attempts
